The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-06-12 albatros_paper.tex
added words on orbcomm synchronization

The back-end readout electronics are housed in a Faraday cage located
50~m away from the antennas. The analog signal chain consists of a
pair of high- and low-pass filters (Minicircuits ZFHP-1R2+ and
SLP-150+) that together band-limit the signal to 1.2--140~MHz, and the
filters are followed by a MiniCircuits ZFL-500+ amplifier.  In
contrast to the two-element pathfinder, the low-pass cutoff is
increased from 81~MHz to 140~MHz to capture downlink signals at
137--138~MHz from the ORBCOMM satellite constellation.
\attention{words here about how we'll use orbcomm for backup timing
  information}

>>>>

The back-end readout electronics are housed in a Faraday cage located
50~m away from the antennas. The analog signal chain consists of a
pair of high- and low-pass filters (Minicircuits ZFHP-1R2+ and
SLP-150+) that together band-limit the signal to 1.2--140~MHz, and the
filters are followed by a MiniCircuits ZFL-500+ amplifier.  In
contrast to the two-element pathfinder, the low-pass cutoff is
increased from 81~MHz to 140~MHz to capture downlink signals at
137--138~MHz from the ORBCOMM satellite constellation.  Preliminary
lab tests suggest that on time scales of 30 seconds, relative timing
between systems can be measured to an accuracy of better than a few
tenths of a nanosecond using a single satellite.  This corresponds to
a phase error at 10 MHz of ~1 degree or less.  With publicly available
orbits and multiple satellites typically within the field of view, we
expect to be able to use ORBCOMM baseband data saved at the same time as the
astronomical data to carry out offline synchronization of the
different ALBATROS stations.
